\sys: Controllable Program Regeneration

### 2025-06-17 paper/draft.tex
Add key results
Signed-off-by: Evangelos Lamprou <vagos@lamprou.xyz>

% \heading{Key results}
% \sys is able to effectively transform programs across a variety goals.

>>>>

\heading{Key results}
\sys is able to effectively transform all programs across the above tasks,
producing high-quality outputs that satisfy user-specified constraints. A total
of six plugins were required to perform the above transformations, each
contributing either a set of extracted and verified properties, or a
transformation, and a set of pre- and post-conditions that the logic engine
uses to construct the regeneration plan.
